Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-16 manuscript/manuscript.Rmd
Add data to package

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library(MASS)
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(magrittr)
library(tidyr)
library(reshape2)
library(scales)
library(grid)
library(geomorph)
library(rjson)
library(ipred)
library(vegan)
library(lubridate)
library(directlabels)
library(BAMMtools)
library(knitcitations)
library(kfigr)
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
source("functions.R")
```

@@

```{r sum_table}
anon_csv <- read_csv("anon.csv")
no_st <- anon_csv %>% filter(role != "student") %>% mutate(role=factor(role), mark=factor(mark), Family = str_replace(fn, "(.{3}).*", "\\1")) %>% select(-fn)

pcaed <- no_st %>% group_by(Family, mark) %>% do(as_df(prcomp(cbind(.$x, .$y), scale=F, center=T)$x, role=as.character(.$role), ident=as.character(.$sha1mac))) %>% mutate(PC1 = as.numeric(PC1), PC2 = as.numeric(PC2))

meds <- pcaed %>% group_by(Family, role, mark) %>% summarise(med=median(PC1)) %>% ungroup() %>% spread(role, med) %>% transmute(Family, mark, value = log(abs(turker - morphologist)), stat="median")

mads <- pcaed %>% group_by(Family, role, mark) %>% summarise(mad=mad(PC1)) %>% ungroup() %>% spread(role, mad) %>% transmute(Family, mark, value = log(turker / morphologist), stat="mad")

@@

<!--
```{r median_tbl, echo=F, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=Family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, echo=F, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=Family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```
-->

@@

subsamp <- group_by(no_st, fn, role) %>% sample_n(size=400) %>% ungroup()

CV <- subsamp %>% group_by(fn) %>% do(estimator = errorest(role ~ mark:x + mark:y, data=., model=lda, estimator="cv", est.para = control.errorest(k=10), predict=ip.lda))

CV_sum <- CV %>% summarise(fn=fn, error=estimator[["error"]]) %>% separate("fn", "fn", sep="_", extra="drop")

CV <- subsamp %>% group_by(fn) %>% do(estimator = errorest(role ~ mark:x + mark:y, data=., model=qda, estimator="cv", est.para = control.errorest(k=10), predict=ip.lda))

CV_sum2 <- CV %>% summarise(fn=fn, qda_error=estimator[["error"]]) %>% separate("fn", "fn", sep="_", extra="drop")

@@

# format for display
CV_sum %>% transmute(`Family`=fn, `LDA`=error, `QDA`=qda_error) %>% knitr::kable(digits=3, caption="Misprediction rate of linear discriminant analysis (LDA) and quadratic discriminant analysis (QDA) with 10-fold cross validation for each fish image.")
```

@@

# Load data from the anonymized results file, remove students, drop bad marks
df <- read_csv("anon.csv") %>%
	filter(role != "student") %>% 
	separate(col=mark, into=c("cat", "cat_seq"), sep=1, remove=F, convert=T) %>%
	mutate(round=floor(sequence/5), fn=factor(str_extract(fn, ".{8}"))) %>%
	filter(!(fn %in% c("Balistid") & mark %in% c("D1","D2")), !mark %in% c("O1","O2","O3","O4","O5", "A3", "D3", "D4"))

# grabs the consensus sequence by person and fish
df <- df %>% group_by(fn, mark, role, sha1mac) %>% summarise(x=median(x), y=median(y))

@@

	res <- as.data.frame(pcdata)
	res$id <- rownames(res)
	res2 <- res %>% separate(id, into=c("fn", "role","sha"), sep="_") %>% tbl_df()

	# consensus in Procrustes space for downstream highlighting
	dots <- list(
		x=lazyeval::interp(~median(axis1, na.rm=T), axis1=as.name(axis1)),
		y=lazyeval::interp(~median(axis2, na.rm=T), axis2=as.name(axis2)))
	consensus <- res2 %>% group_by(fn, role) %>% summarise_(.dots=dots)

	p <- ggplot(res2, aes_string(axis1, axis2, group="fn")) + geom_point(aes(col=fn, shape=role)) + geom_point(aes(x, y), data=consensus, alpha=0.5, size=5, col="black") + geom_point(aes(x, y, col=fn, shape=role), data=consensus) + stat_ellipse(aes(color=fn), linetype=2, type="norm", level=0.95) + theme_minimal() + theme(legend.position="none")

@@

We attempted to distinguish between turker-generated landmarks and expert-generated landmarks using linear discriminant analysis. Even the image with the lowest misprediction rate, from the family `r filter(CV_sum, min(error) == error)$fn`, still incorrectly predicted the digitizer's identity `r filter(CV_sum, min(error) == error)$error %>% as.numeric() %>% scales::percent()` of the time, suggesting that, given a set of landmarks, it is difficult to predict whether a turker or a morphologist created them. The quadratic discriminant analysis did not reliably improve prediction of worker identity over the LDA.

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitcitations")
library("kfigr")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_landmarks)
```

@@

```{r sum_table}
no_st <- fish_landmarks %>% filter(role != "student")

pcaed <- no_st %>% group_by(family, mark) %>% do(as_df(prcomp(cbind(.$x, .$y), scale=F, center=T)$x, role=as.character(.$role), ident=as.character(.$sha1mac))) %>% mutate(PC1 = as.numeric(PC1), PC2 = as.numeric(PC2))

meds <- pcaed %>% group_by(family, role, mark) %>% summarise(med=median(PC1)) %>% ungroup() %>% spread(role, med) %>% transmute(family, mark, value = log(abs(turker - morphologist)), stat="median")

mads <- pcaed %>% group_by(family, role, mark) %>% summarise(mad=mad(PC1)) %>% ungroup() %>% spread(role, mad) %>% transmute(family, mark, value = log(turker / morphologist), stat="mad")

@@

<!--
```{r median_tbl, echo=F, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, echo=F, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```
-->

@@

subsamp <- group_by(no_st, family, role) %>% sample_n(size=400) %>% ungroup()

CV <- subsamp %>% group_by(family) %>% do(estimator = errorest(role ~ mark:x + mark:y, data=., model=lda, estimator="cv", est.para = control.errorest(k=10), predict=ip.lda))

CV_sum <- CV %>% summarise(family=family, error=estimator[["error"]]) %>% separate("family", "family", sep="_", extra="drop")

CV <- subsamp %>% group_by(family) %>% do(estimator = errorest(role ~ mark:x + mark:y, data=., model=qda, estimator="cv", est.para = control.errorest(k=10), predict=ip.lda))

CV_sum2 <- CV %>% summarise(family=family, qda_error=estimator[["error"]]) %>% separate("family", "family", sep="_", extra="drop")

@@

# format for display
CV_sum %>% transmute(`Family`=family, `LDA`=error, `QDA`=qda_error) %>% knitr::kable(digits=3, caption="Misprediction rate of linear discriminant analysis (LDA) and quadratic discriminant analysis (QDA) with 10-fold cross validation for each fish image.")
```

@@

# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_landmarks %>%
	filter(role != "student") %>% 
	separate(col=mark, into=c("cat", "cat_seq"), sep=1, remove=F, convert=T) %>%
	filter(!(family %in% c("Bal") & mark %in% c("D1","D2")), !mark %in% c("O1","O2","O3","O4","O5", "A3", "D3", "D4"))

# grabs the consensus sequence by person and fish
df <- df %>% group_by(family, mark, role, sha1mac) %>% summarise(x=median(x), y=median(y))

@@

	res <- as.data.frame(pcdata)
	res$id <- rownames(res)
	res2 <- res %>% separate(id, into=c("family", "role","sha"), sep="_") %>% tbl_df()

	# consensus in Procrustes space for downstream highlighting
	dots <- list(
		x=lazyeval::interp(~median(axis1, na.rm=T), axis1=as.name(axis1)),
		y=lazyeval::interp(~median(axis2, na.rm=T), axis2=as.name(axis2)))
	consensus <- res2 %>% group_by(family, role) %>% summarise_(.dots=dots)

	p <- ggplot(res2, aes_string(axis1, axis2, group="family")) + geom_point(aes(col=family, shape=role)) + geom_point(aes(x, y), data=consensus, alpha=0.5, size=5, col="black") + geom_point(aes(x, y, col=family, shape=role), data=consensus) + stat_ellipse(aes(color=family), linetype=2, type="norm", level=0.95) + theme_minimal() + theme(legend.position="none")

@@

We attempted to distinguish between turker-generated landmarks and expert-generated landmarks using linear discriminant analysis. Even the image with the lowest misprediction rate, from the family `r filter(CV_sum, min(error) == error)$family`, still incorrectly predicted the digitizer's identity `r filter(CV_sum, min(error) == error)$error %>% as.numeric() %>% scales::percent()` of the time, suggesting that, given a set of landmarks, it is difficult to predict whether a turker or a morphologist created them. The quadratic discriminant analysis did not reliably improve prediction of worker identity over the LDA.
